Comparing R packages for calculation of persistent homology

### 2020-03-19 tdabench-paper/tdabench.Rmd
corrected phrasing
correct library name

\section{Discussion}
As persistent homology calculations continue to become a more popular tool to analyze complex multidimensional data, it will be important to understand from a computational perspective which method to use. 
In this paper, we examined two forms of persistent homology complexes: Vietoris-Rips and alpha complexes. 
Both algorithms describe topological features through the generation of simplicial complexes. 
The advantage in saving computational time in choosing a particular algorithm depends on the point cloud characteristics.

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex calculations outperforms TDAstats. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially. 
Specifically, alpha complexes are $O(n^\frac{d}{2})$ and Vietoris-Rips complexes are $O(2^n)$ where n is the number of points on a point cloud and d is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoritical maximums. 
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.

>>>>

\section{Discussion}
As persistent homology calculations continue to become a more popular tool to analyze complex multidimensional data, it will be important to understand from a computational perspective which method to use. 
In this paper, we examined two forms of persistent homology complexes: Vietoris-Rips and alpha complexes. 
Both algorithms describe topological features through the generation of simplicial complexes. 
The advantage in saving computational time by choosing a particular algorithm depends on point cloud characteristics.

Figure \ref{fig:fin} shows that at high point cloud sizes, GUDHI’s alpha complex outperforms Ripser. 
Theoretically, alpha complexes gain polynomial complexity as the number of points increases whereas Vietoris-Rips complexes gain exponentially. 
Specifically, alpha complexes are $O(n^\frac{d}{2})$ and Vietoris-Rips complexes are $O(2^n)$ where n is the number of points on a point cloud and d is the dimensions on the point cloud. 
For the conditions in our paper, Vietoris-Rips and alpha complexes both performed better than their theoritical maximums. 
Vietoris-Rips complex calculations consistently had a polynomial growth for both runtime and boundary matrix size while alpha complexes had linear growth.
